The shape of kelp: environmental influences on kelp morphology

### 2018-10-18 chapter_2.Rmd
sorted out issue of multiple graphs plotting for temperature

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Wave roses of the Cape Point wave rider buoy situated at 18.29oE, 34.2oS in 70m water depth. (a) total wave record, (b) winter waves and (c) summer waves."}

@@

grid.arrange(img_twr, img_wwr,img_swr, ncol = 3)

@@

kable(morph_eck, row.names = FALSE, caption = "A list of morphology measurements that were collected to investigate how environmental drivers may influence the morphology of _Ecklonia maxima _. Units for each morphometric are included.")

@@

kable(morph_lam, row.names = FALSE, caption = "A list of morphology measurements that were collected to investigate how environmental drivers may influence the morphology of _Laminaria pallida_. Units for each morphometric are included.")

@@

## Subset temperatures for collection sites
temps <- SACTNmonthly_v4.1 %>% 
  filter(site %in% eck_data$site | site %in% lam_data$site) %>% 
  select(site, date, temp) %>% 
  rbind(., interp_sites) %>% 
  filter(site!= "Roman Rock") %>% 
  rbind(., rr_patch)
```

```{r, echo= FALSE, message=FALSE, warning=FALSE, results='hide'}

@@

```{r, echo= FALSE, message=FALSE, warning=FALSE}
# Merge site list with temp_clim
site_temp <- merge(temp_clim, kelp_sites, by = "site")

@@

```{r, echo= FALSE, message=FALSE, warning=FALSE, fig.cap="Morphometric site locations represented by various temperature parameters. Temperature parameters include minimum, maximum and mean temperatures (° Celsius). These site locations are coloured by the temperature statistic relative to the legends provided. Each temperature parameter is also divided into August (winter) and February (summer) as well as the annual mean.", fig.height=8, fig.width=12, fig.pos="H"}

grid.arrange(min, max, mean, ncol = 1)
ggarrange(min, max, mean, ncol = 1, nrow = 1, labels = "AUTO", legend = "bottom", common.legend = TRUE, align = "none", heights = c(1.5,1))
```

```{r, echo= FALSE, message=FALSE, warning=FALSE, fig.cap="Morphometric site locations represented by various temperature parameters. Temperature parameters include temperature range as well as standard deviation (° Celsius). These site locations are coloured by the temperature statistic relative to the legends provided. Each temperature parameter is also divided into August (winter) and February (summer) as well as the annual mean.", fig.height=8, fig.width=12, fig.pos="H"}

grid.arrange(range, sd, ncol = 1)

@@

## MEthod 2 (shows individual legends, still squashed)

@@

grid.arrange(medianDir1, meanHs1, sdHs1, meanTp1, sdTp1)

@@

grid.arrange(medianDirw1, meanSpw1, sdSpw1)

@@

# Order site names by location west to east
positionsEck <- c("Betty's Bay", "Kalk Bay", "A-Frame", 
                  "Miller's Point", "Baboon Rock", "Batsata Rock", 
                  "Buffels Bay", "Scarborough", 
                  "Soetwater","Kommetjie","Hout Bay", 
                  "Oudekraal", "St. Helena Bay")

>>>>

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Wave roses of the Cape Point wave rider buoy situated at 18.29oE, message=FALSE, warning=FALSE, 34.2oS in 70m water depth. (a) total wave record, (b) winter waves and (c) summer waves."}

@@

grid.arrange(img_twr, img_wwr,img_swr, ncol = 2, nrow = 2)

@@

t1 <- kable(morph_eck, row.names = FALSE, caption = "A list of morphology measurements that were collected to investigate how environmental drivers may influence the morphology of _Ecklonia maxima _. Units for each morphometric are included.")

@@

t2 <- kable(morph_lam, row.names = FALSE, caption = "A list of morphology measurements that were collected to investigate how environmental drivers may influence the morphology of _Laminaria pallida_. Units for each morphometric are included.")

@@

## Subset temperatures for collection sites
temps <- SACTNmonthly_v4.1 %>% 
  filter(site %in% eck_data$site | site %in% lam_data$site) %>% 
  select(site, date, temp) %>% 
  rbind(., interp_sites) %>% 
  filter(site!= "Roman Rock") %>% 
  rbind(., rr_patch)
```
```{r, echo= FALSE, message=FALSE, warning=FALSE, results='hide'}

@@

```
```{r, echo= FALSE, message=FALSE, warning=FALSE}
# Merge site list with temp_clim
site_temp <- merge(temp_clim, kelp_sites, by = "site")

@@

```{r, echo= FALSE, message=FALSE, warning=FALSE, fig.cap="Morphometric site locations represented by various temperature parameters. Temperature parameters include minimum, maximum, mean, range and standard deviation (° Celsius). These site locations are coloured by the temperature statistic relative to the legends provided. Each temperature parameter is also divided into August (winter) and February (summer) as well as the annual mean.", fig.height=8, fig.width=12, fig.pos="H"}

grid.arrange(max,min,mean,range, sd, ncol = 2)

@@

##  (shows individual legends, still squashed)

@@

grid.arrange(medianDir1, meanHs1, sdHs1, meanTp1, sdTp1, ncol = 2)

@@

grid.arrange(medianDirw1, meanSpw1, sdSpw1, ncol = 2)

@@

# Order site names by location west to east

positionsEck <- c("Betty's Bay", "Kalk Bay", "A-Frame", 
                  "Miller's Point", "Baboon Rock", "Batsata Rock", 
                  "Buffels Bay", "Scarborough", 
                  "Soetwater","Kommetjie","Hout Bay", 
                  "Oudekraal", "St. Helena Bay")
